\chapter*{Preface}

Quantum networks and quantum computing have created a significant amount of excitement and interest in the technical community. As with any emerging technology, there is a lot of potential opportunity in the exploitation of that technology, but frequently the implications of the technology are over-inflated and difficult to pinpoint. A significant amount of confusion also arises due to the high degree of specialization that exists in the present technical community, making it difficult to assess and evaluate the benefits of new technology. 

There are many books existing on quantum networks, but most of them are geared towards the physicists and theoreticians working on improving the quantum communication technologies. That leaves many software professionals and computer scientists wondering about the implications of these networks, and what impact they may have on the future of information technology. 

This book attempts to bridge that gap that exists, providing an overview of the quantum networks from the perspective of a software user. It discusses the current state of quantum networks, how it compares to the traditional computer networks, and what type of software applications would benefit from the use of quantum networks. 

We hope the simplified approach to deal with quantum networking technologies in this book will be useful to the software engineer, as well as the CTOs and CIOs in many enterprises as they try to assess the impact of quantum technologies on their businesses. 
